Pretty darn good control: when are approximate solutions better than approximate models

### 2023-01-24 manuscript/manuscript.Rmd
added escapement timeseries

>>>>

```{r escapement_timeseries, fig.cap = "TBD", out.width = "6.5in"}

ppo_mod <- ppo |> 
  mutate(X = X+1, Y = Y+1, Z = Z+1, escapement = (1-action)*X, time = t)

avg_esc <- mean(ppo_mod$escapement)
# = 0.6201131

ppo_esc <- ppo_mod |>
  filter(rep==0) |>
  group_by(rep) |>
  ggplot(aes(time, escapement), alpha = rep) +
  geom_line() +
  geom_hline(aes(yintercept=avg_esc), color="red")+
  theme(aspect.ratio = 1/5)

ppo_esc
```
